Model Search in Relational Domains

### 2016-10-20 learning.tex
section 6

\section{Abstract Conflict Analysis}
A conflict analysis in a SAT solver can be seen as abductive 
reasoning which underapproximate a set of models that do not satisfy a 
formula~\cite{sas12,dhk2013-popl}.  
\Omit {
where a singleton assignment $c$ is replaced by a partial 
assignment that is sufficient to infer $c$.  Thus, a conflict 
analysis is a generalization of an under-approximation of a set of 
countermodels, where a countermodel is a 
set of structures that do not satisfy a formula 
}
Since relational abstract domains have more complex structure than a partial 
assignments domain or interval domain, so the generalization of {\em first-UIP} algorithm~\cite{uip} and clause learning in a relational lattice structure is non-trivial.

>>>>

\section{Abstract Conflict Analysis}
A conflict analysis in a SAT solver can be seen as abductive 
reasoning which underapproximate a set of models that do not satisfy a 
formula~\cite{sas12,dhk2013-popl}.  
\Omit {
where a singleton assignment $c$ is replaced by a partial 
assignment that is sufficient to infer $c$.  Thus, a conflict 
analysis is a generalization of an under-approximation of a set of 
countermodels, where a countermodel is a 
set of structures that do not satisfy a formula 
}
Since relational abstract domains have more complex structure than a partial 
assignments domain or interval domain, so finding a generalized reason for 
conflict through UIP computation~\cite{uip} is non-trivial.
